In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-10 paper/main.tex
fix beta_exit
fix table 1 units

      Molecular efflux rate & $\beta_{\rm exit}$ & $10^{-4}$ & mm$^2$/s & \cite{hornkjol2022csf} \\

@@

      CSF production rate & $u_{\mathrm{in}}$ & $0.63$  & l / day & \cite{nilsson1992circadian} \\

@@

      CSF outflow resistance & $R_0$ & $10^{-5}$  & Pa/(mm$\cdot$s) & \cite{hornkjol2022csf} \\ 

>>>>

      Molecular efflux rate & $\beta_{\rm exit}$ & $8\cdot 10^{-7}$ & m/s & \cite{hornkjol2022csf} \\

@@

      CSF production rate & $u_{\mathrm{in}}$ & $0.4$  & l / day & \cite{nilsson1992circadian} \\

@@

      CSF outflow resistance & $R_0$ & $10^{4}$  & Pa$\cdot$s/m & \cite{hornkjol2022csf} \\ 
